Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events

### 2016-06-20 Manuscript/MS- What is LDD.tex
Added Table 2 and edited figure legends,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS Draft Journal of Ecology Special Issue, Dispersal - 
%% Pedro - 07 April 2016
%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Headers
\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\pagestyle{plain}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{lscape}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{rotating}                                                                                    
\newcommand{\tab}{\hspace{5mm}}
\usepackage{tabularx} 
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage[left]{lineno}
\usepackage{caption}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy}     % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{{\tiny Jordano - What is long-distance dispersal?}}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}
\usepackage{parskip}
\linespread{1.25}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page
\begin{document}

@@

@@

@@

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the four combinations of \textit{Prunus mahaleb} seed dispersal events outlined in Table 1. These result from dissemination within (yellow) and outside (blue) the population geographic limits ($SDD_{loc}$, $LDD_{loc}$, respectively) and/or the genetic neigborhood area limits ($SDD_{neigh}$, $LDD_{ss}$, respectively).\\ 
\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS Draft Journal of Ecology Special Issue, Dispersal - 
%% Pedro - 07 April 2016
%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Headers
\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\pagestyle{plain}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{lscape}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{rotating}                                                                                    
\newcommand{\tab}{\hspace{5mm}}
\usepackage{tabularx} 
%\usepackage{multirow}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage[left]{lineno}
\usepackage{caption}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy}     % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{{\tiny Jordano - What is long-distance dispersal?}}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}
\usepackage{parskip}
\linespread{1.25}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page
\begin{document}

@@

%-------------------------------------------------------------------- Table 2
\pagestyle{empty}
\begin{landscape}
\begin{table}
\captionsetup{width=21cm}%.75\textwidth}
\caption{Frequencies of \textit{Prunus mahaleb} seed dispersal events for different frugivore groups according to population area limits and genetic neighborhood limits. See Fig. 2 for a graphical representation of the four scenarios.}
\vspace{0.5cm}
    \begin{tabular}{lp{3cm}p{3cm}p{3cm}p{3cm}}
    \hline \\
    Frugivore group & Within-population, within-neighborhood $SSD_{loc}$ & Within-population, long-distance $LDD_{loc}$ & Outside-population, within-neighborhood $LDD_{neigh}$ & Strict-sense long-distance $LDD_{ss}$ \\\\ \hline \\
    Small birds     & ?~           & ?~            & ?~           & ?~  \\
    \textit{Turdus} & ?~           & ?~            & ?~           & ?~  \\

    Large birds     & ?~           & ?~            & ?~           & ?~  \\

    Mammals         & ?~           & ?~            & ?~           & ?~  \\\\
\hline
    \end{tabular}
\end{table}
\end{landscape}

@@

\newpage  
\newpage

@@

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the four combinations of \textit{Prunus mahaleb} seed dispersal events outlined in Table 1. These result from dissemination within (yellow) or outside (blue) the population geographic limits ($SDD_{loc}$, $LDD_{loc}$, respectively) and within or outside the genetic neigborhood area limits ($SDD_{neigh}$, $LDD_{ss}$, respectively).\\ 
\newpage
